Reliable error estimation for Sobol' indices

### 2016-08-12 article.tex
Modifying the description of the estimators in article.tex

\subsection{Reliable Estimation Using Quasi-Monte Carlo}

@@

\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$. In both cases, regular and normalized indices can be approximated by estimating some integrals,
\begin{align*}
\underline{S}_u & = \frac{\int_{[0,1)^{2d-1}} f(\vx)f(\vx_{u}:{\vx'}_{-u})d\vx d{\vx'} - \mu^2 }{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1-(I_3)^2}{I_2-(I_3)^2}, \\
\overline{S}_u & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1}{I_2-(I_3)^2}.
\end{align*}
Therefore, we can define $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$. If we can estimate $\vI$ such that $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$, then we can define the following estimators for the Sobol' indices:
\begin{align*}
\widehat{S}_u & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right) \\
\varepsilon_{S_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} S_u(\vI),0\right) \right)
\end{align*}
where the true value $S_u\in [\widehat{S}_u - \varepsilon_{S_u}, \widehat{S}_u + \varepsilon_{S_u}]$.
\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{Images/scheme_S.eps}
\end{figure}

>>>>

\subsection{Reliable Estimation Using Quasi-Monte Carlo}
\label{section.error.algo}

@@

\subsection{Definition of $\widehat{S}$ (fix it with max and min)}
In some applications, it is more useful to estimate the normalized Sobol' indices, $S_u = \underline{\tau}_u^2/\sigma^2$ and $\overline{S}_u = \overline{\tau}_u^2/\sigma^2$. In both cases, regular and normalized indices can be approximated by estimating some integrals,
\begin{align*}
\underline{S}_u & = \frac{\int_{[0,1)^{2d-1}} \left(f(\vx)-
f(\vx_u:{\vx'}_{-u})\right)f(\vx')d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_1}{I_3-(I_4)^2}, \\
\overline{S}_u & = \frac{\frac{1}{2}\int_{[0,1)^{d+1}}(f(\vx')-f(\vx_u:{\vx'}_{-u}))^2d\vx d{\vx'}}{\int_{[0,1)^{d}} f(\vx)^2 d{\vx}-\mu^2} = \frac{I_2}{I_3-(I_4)^2}.
\end{align*}
If $\vI:=(I_1,I_2,I_3,I_4)$, we can define $\underline{S}_u(\vI)$ and $\overline{S}_u(\vI)$ as functions over a vector of integrals $\vI$. If we estimate $\vI$ by $\widehat{\vI}$ and error bound $\varepsilon_{\vI}$ according to \ref{section.error.algo}, then $\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI}):=[\widehat{\vI}-\varepsilon_{\vI},\widehat{\vI}+\varepsilon_{\vI} ]$.

Alternatively to the common estimators $\widehat{\underline{S}_u}=\underline{S}_u(\widehat{\vI})$ and $\widehat{\overline{S}_u}=\overline{S}_u(\widehat{\vI})$, we propose the following estimators:
\begin{align*}
\widehat{\underline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\right) \right), \\
\varepsilon_{\underline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \underline{S}_u(\vI),0\right) \right),
\end{align*}
and,
\begin{align*}
\widehat{\overline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\right) + \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\right) \right), \\
\varepsilon_{\overline{S}_u} & = \frac{1}{2}\left(\min\left(\max_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),1\right) - \max\left(\min_{\vI\in B_{\varepsilon_{\vI}}(\widehat{\vI})} \overline{S}_u(\vI),0\right) \right).
\end{align*}
These new estimators allow us to say that $\underline{S}_u\in [\widehat{\underline{S}_u} - \varepsilon_{\underline{S}_u}, \widehat{\underline{S}_u} + \varepsilon_{\underline{S}_u}]$ and $\overline{S}_u\in [\widehat{\overline{S}_u} - \varepsilon_{\overline{S}_u}, \widehat{\overline{S}_u} + \varepsilon_{\overline{S}_u}]$.

For a better understanding of these estimators, we provide and example in dimension 1 below,
\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{Images/scheme_S.eps}
\end{figure}
